How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-11 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Add matrix of total points, and plot of time taken #22

@@

```{r}
read_sk <- function(s, k) {
  assign(paste0("s", s, "k", k), readRDS(paste0("depends/aghq-s", s, "-k", k, ".rds"))$quad, envir = parent.frame())
}

@@

```{r}
stopifnot(nrow(s5k2$modesandhessians) == 2^5)
stopifnot(nrow(s3k3$modesandhessians) == 3^3)
```

@@

df <- data.frame(
  s = rep(1:5, times = 2),
  k = rep(2:3, each = 5),
  lognormconst = sapply(c(k2, k2), function(x) x$normalized_posterior$lognormconst)
)

@@

>>>>

# What might be possible?

```{r}
k_seq <- seq(1, 15, by = 2)
s_seq <- 1:10

M <- matrix(0, length(k_seq), length(s_seq))

for (i in 1:length(k_seq)) {
	for (j in 1:length(s_seq)) {
		M[i, j] <- k_seq[i]^(s_seq[j])
  }
}

# Assume anything more than a million isn't possible
M[M > 1e6] <- NA
```

@@

```{r}
read_sk <- function(s, k) {
  assign(paste0("s", s, "k", k), readRDS(paste0("depends/aghq-s", s, "-k", k, ".rds"))[c("quad", "time")], envir = parent.frame())
}

@@

```{r}
stopifnot(nrow(s5k2$quad$modesandhessians) == 2^5)
stopifnot(nrow(s3k3$quad$modesandhessians) == 3^3)
```

@@

df <- data.frame(
  s = rep(1:5, times = 2),
  k = rep(2:3, each = 5),
  lognormconst = sapply(c(k2, k3), function(x) x$quad$normalized_posterior$lognormconst),
  time = sapply(c(k2, k3), function(x) x$time)
)

@@

```{r}
ggplot(df, aes(x = s, y = time)) +
  geom_point() +
  facet_grid(. ~ k) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Dimensions kept of the PCA", y = "Time (mins)") +
  theme_minimal()
```
